---
title: "DSC 520 Final Project"
author: "Lara Clasen"
date: "6/1/2019"
output: html_document
---


```{r include=FALSE}
library(readr)
library(ggplot2)
library(pastecs)
library(DataExplorer)
library(dplyr)
```

First I read in my Excel document containing the data sat I obtained from the State of Minnesota.
The data dictionary for this data can be found in the State of Minnesota Data Tool (https://apps.deed.state.mn.us/lmi/etd/Results.aspx).

```{r}
mydata <- read.csv("schooldata.csv")
head(mydata)
```

I need to adjust my data types so that I can analyze them. I change the percentage values to numeric and remove the dollar signs and commas from the currency values.

```{r}
mydata$WFT2 <- as.numeric(gsub('\\$|,', '', mydata$WFT2))
mydata$WFT3 <- as.numeric(gsub('\\$|,', '', mydata$WFT3))
mydata$WFT4 <- as.numeric(gsub('\\$|,', '', mydata$WFT4))
mydata$PFT2 <- as.numeric(mydata$PFT2)
mydata$PFT3 <- as.numeric(mydata$PFT3)
mydata$PFT4 <- as.numeric(mydata$PFT4)

head(mydata)
str(mydata)
dim(mydata)
glimpse(mydata)
stat.desc(mydata)
summary(mydata)
```

Next is to obtain some visual representation of the data.

```{r} 
ggplot(mydata, aes(x = Instructional.Program.Title, y = PFT2)) + geom_point()
ggplot(mydata, aes(x = Instructional.Program.Title, y = PFT3)) + geom_point()
ggplot(mydata, aes(x = Instructional.Program.Title, y = PFT4)) + geom_point()

ggplot(data = mydata, mapping = aes(x = WFT2, y = WFT4)) +
  geom_point(mapping = aes(color = Instructional.Program.Title)) +
  geom_smooth()

```

I want to fit a regression model on the data.

```{r}
model1 <- lm(WFT4 ~ WFT2, data = mydata)
model1

summary(model1)
```

This translates to a regression of Wages after Year 4 on Wages after Year 2. According to our model, for every additional dollar amount earned after 2 years working full-time, we expect an additional 0.9995 earned in the 4th year after graduation while working full-time. This tells us that it does matter to obtain a higher-paying position just after graduation, but it may not matter all that much.


The Data Explorer report is also attached, which was produced using the following code:
DataExplorer::create_report(mydata)

